%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\name{ARIELLA GLADSTEIN, PhD} % Your name
%\address{} % Your address
\address{algladstein@gmail.com} % Your phone number and email
% \address{\small \url{https://ariella-gladstein.netlify.app}  \\ \url{https://github.com/agladstein} \\ \url{www.linkedin.com/in/ariella-gladstein}} % Your phone number and email
\address{\small \url{https://github.com/agladstein} \\ \url{www.linkedin.com/in/ariella-gladstein}} % Your phone number and email
\renewenvironment{rSection}[1]{
\sectionskip
\textcolor{RoyalPurple}{\MakeUppercase{#1}}
\sectionlineskip
\hrule
\begin{list}{}{
\setlength{\leftmargin}{1.5em}
}
\item[]
}{
\end{list}
}

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\textcolor{RoyalPurple}{\bf Expertise:}
\textcolor{RoyalPurple}{\em population genetics, genomics, computational biology, data science, machine learning, statistics}

\begin{rSection}{Education}

{\bf University of Arizona, Tucson, AZ} \hfill {\em August 2018} \\ 
PhD in Ecology and Evolutionary Biology, Minor in Mathematics 

{\bf Beloit College, Beloit, WI} \hfill {\em May 2011} \\ 
B.S. in Mathematical Biology \& Russian, Cum Laude \\
Departmental Honors: Mathematical Biology

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

{\bf Open Source Contributor} \hfill  2024 - present\\ 
{\em Tskit community} \hfill {\em Remote}\\
Contirbuted to writing and reviewing documentation and tutorials for the population genomics tskit ecosytem.

{\bf Research Scientist, Computational Biology} \hfill  2021 - 2024\\ 
{\em Ancestry team} \hfill {\em Embark Veterinary, Remote}\\
Developed dog breed ancestry and relative-matching products, enhancing computational efficiency while maintaining rigorous quality standards. Played a key role in improving pipeline automation from 40\% to over 95\% within one year and scaling processes from hundreds of thousands to millions of samples. Collaborated with a cross-functional team on a science initiative projected to save \$7.5 million annually. Served on the Diversity, Equity, Inclusion, and Belonging (DEIB) committee, co-authoring an Inclusive Norms document, designing and analyzing company-wide DEIB surveys, and contributing to various DEIB initiatives.

{\bf Postdoctoral Fellowship} \hfill  2018 - 2020\\ 
{\em Schrider Lab} \hfill {\em Department of Genetics, University of North Carolina, Chapel Hill}\\
Developed deep learning models for population genetics inference. Contributed to writing documentation and tutorials for the population genomics tskit software ecosystem. Actively participated in the PopSim Consortium, contributing to the development of the stdpopsim library.


{\bf Dissertation Research} \hfill  2011 - 2018\\ 
{\em Hammer Lab} \hfill {\em Ecology and Evolutionary Biology, University of Arizona}\\
Developed and applied computational methods for population genetics analysis, addressing ascertainment bias in identifying runs of homozygosity and demographic inference. Created and released software for high-throughput genomic simulations. Applied Approximate Bayesian Computation (ABC) to model the demographic history of Ashkenazi Jews.

{\bf Functional Genomics Research Rotation} \hfill  Spring 2012\\ 
{\em Restifo Lab} \hfill {\em Neuroscience, University of Arizona}

{\bf Computational Genomics Research Rotation} \hfill  Fall 2011\\ 
{\em Kececioglu Lab} \hfill {\em Computer Science, University of Arizona}

{\bf Lab technician intern} \hfill  Sp, Fall 2009\\ 
{\em Laboratory of Population Genetics} \hfill {\em Russian Academy of Medical Sciences, Moscow, Russia}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Skills
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming & Python, R, Bash, unit testing, profiling, multiprocessing, Git\\
HPC/HTC \& Cloud & Linux/Unix, SLURM, PBS, AWS, JupyterHub, Kubernetes  \\
Genomics & PLINK, Bedtools, VCFtools, phasing, imputation, haplotype detection, population \\ & structure, genome simulation\\
Data Science & Numpy, Pandas, Scikit-learn, SciPy, Keras, Matplotlib, Seaborn, Plotly, ggplot \\
Reproducibility & Workflow development (Pegasus, Makeflow, Snakemake), containers \\ & (Singularity, Docker), virtual environments, Jupyter, Knitr \\
Documentation & \LaTeX, Markdown, reStructuredText, JupyterBook, Confluence \\
Mathematical Skills & Probability theory, statistical inference, linear algebra \\
Language Skills & English (native speaker), Russian (fluent) \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Teaching Experience
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}

    {\bf Introduction to using stdpopsim Workshop} \hfill 2020, {\em Virtual, PopSim Consortium} \\ 
    {\em Designed and presented interactive workshop on using stdpopsim, the standard library for reproducible, bug-free simulations of genetic datasets from published demographic histories.}

    {\bf NSF Cyber Carpentry Workshop} \hfill 2019, {\em University of North Carolina, Chapel Hill} \\ 
    {\em Assisted with 2-week workshop, where participants learned best practices for data-intensive computing, cloud infrastructure, and deep learning through hands-on projects.}

    {\bf Research Bazaar Workshop on R} \hfill 2018, {\em University of Arizona} \\ 
    {\em Assisted with hands-on intro R workshop}

    {\bf CyVerse Container Camp} \hfill 2018, {\em University of Arizona} \\ 
    {\em Assisted with 3-day hands-on workshop on using containerized workflows for more reproducible science.}

    {\bf Software Carpentry Workshop} \hfill 2017, {\em University of Arizona} \\ 
    {\em Assisted with Software Carpentry hands-on workshop on basic Unix/Bash, Python, and Git}

    {\bf Tucson Women’s Hackathon workshop on Git} \hfill 2017, {\em University of Arizona} \\ 
    {\em Assisted with hands-on workshop on basic Git}

    {\bf ECOL 320 Genetics} \hfill 2014 - 2016, {\em University of Arizona} \\ 
    {\em Graduate Teaching Assistant}

    {\bf ECOL 182L Intro to Ecology and Evolutionary Biology Lab} \hfill 2015, {\em University of Arizona} \\ 
    {\em Graduate Teaching Assistant}

    {\bf Population Genetics Module} \hfill 2013, {\em Kino School} \\ 
    {\em Developed and taught a 3-day module on population genetics to high schoolers.}

    {\bf BIOL 247 Biometrics} \hfill 2011, {\em Beloit College} \\ 
    {\em Teaching Assistant}

    {\bf RUSS 110, 115, 210, 215 Russian} \hfill 2009 - 2011, {\em Beloit College} \\ 
    {\em Tutor}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

\item Lauterbur, M. E., Cavassim, M. I. A., \textbf{Gladstein, A. L.}, $\ldots$, Wong, Y., Baumdicker, F., Cartwright, R. A., Gorjanc, G., Gutenkunst, R. N., Kelleher, J., Kern, A. D. Ragsdale, A. P., Ralph, P. L., Schrider, D. R., Gronau, I. 2023. Expanding the stdpopsim species catalog, and lessons learned for realistic genome simulations \textit{eLife} 12:RP84874. \url{https://doi.org/10.7554/eLife.84874.3}

\item Baumdicker, F.*, Bisschop, G.*, Goldstein, D.*, Gower, G.*, Ragsdale, A. P.*, Tsambos, G.*, Zhu, S.*, $\ldots$, \textbf{Gladstein, A. L.}, $\ldots$, Kelleher, J. 2022. Efficient ancestry and mutation simulation with msprime 1.0. \textit{Genetics}. Volume 220, Issue 3. \url{https://doi.org/10.1093/genetics/iyab229}

\item Adrion, J. R.*, Cole, C. B.*, Dukler, N.*, Galloway, J. G.*, \textbf{Gladstein, A. L.}\footnote{First author}, Gower, G.*, Kyriazis, C.C.*, Ragsdale, A.P.*, Tsambos, G.*, $\ldots$, Gravel, S., Gutenkunst, R.N., Lohmeuller, K.E., Ralph, P.L., Schrider, D.R., Siepel, A., Kelleher, J., Kern, A.D. 2020. A community-maintained standard library of population genetic models. \textit{eLife}. 9:e54967. doi: \url{https://doi.org/10.1101/2019.12.20.885129}

\item Bernstein M.N.*, \textbf{Gladstein A.}, Latt K.Z. et al. Jupyter notebook-based tools for building structured datasets from the Sequence Read Archive [version 2; peer review: 2 approved]. F1000Research 2020. 9:376. doi: \url{https://doi.org/10.12688/f1000research.23180.2}

\item \textbf{Gladstein A.L.}* and Hammer M.F. 2019. Substructured population growth in the Ashkenazi Jews inferred with Approximate Bayesian Computation. \textit{Molecular Biology and Evolution}. 36(6): 1162-1171. doi: \url{https://dx.doi.org/10.1093/molbev/msz047}

\item \textbf{Gladstein A.L.}* et al. 2018. SimPrily: A Python framework to simplify high-throughput genomic simulations. \textit{SoftwareX}, 7, 335-340. \url{https://doi.org/10.1016/j.softx.2018.09.003}

%\item Gladstein A.L., Watkins J., and Hammer, M.F. 2018. Reliability of runs of homozygosity detection from SNP arrays depends on algorithmic choices. (in preparation).

\item \textbf{Gladstein A.}* and Hammer M.F. 2016. Population Genetics of the Ashkenazim. In: \textit{eLS}. John Wiley \& Sons, Ltd: Chichester. pp. 1-8. \url{https://doi.org/10.1002/9780470015902.a0020818.pub2}

\item Behar D.* et al. 2013. No evidence from genome-wide data of a Khazar origin for the Ashkenazi Jews. \textit{Human Biology}. 85.6:859-900. \url{https://doi.org/10.3378/027.085.0604}

\item \textbf{Gladstein A.L.}* 2011. Split decomposition analysis groups Jewish populations together between European and Middle Eastern populations. \textit{The Beloit Biologist}. 30:29-36.

\end{rSection}

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\begin{rSection}{Posters and Presentations}

\textbf{Invited Talks}
\item  Deep learning for demographic model choice. Human Evolutionary and Population Genomics Seminar. 2020. LANGEBIO, UGA-Cinvestav. Irapuato-Guanajuato, Mexico (virtual).

\item Inference of evolutionary history with Approximate Bayesian Computation. Open Science Grid All-Hands Meeting. 2018. Salt Lake City, Utah.

\item Code optimization for research scientists. Research Bazaar. 2018. Tucson, AZ.

\textbf{Posters}

\item \textbf{Gladstein A.L.}\footnote{Presenter}, et al. A Novel Machine Learning Method for Classification of Village Dogs.  Probabilistic Modeling in Genomics. 2023. Cold Spring Harbor, NY.

\item \textbf{Gladstein A.L.}\textsuperscript{\textdagger}, Schrider R.D.  Demographic model selection with deep learning.  Probabilistic Modeling in Genomics. 2019. Aussois, France.

\item \textbf{Gladstein A.L.}\textsuperscript{\textdagger}, Hammer M.F. Substructured population growth in the Ashkenazi Jews inferred with Approximate Bayesian Computation. UNC Women in Computing Research Symposium. 2019. Chapel Hill, NC.

\item \textbf{Gladstein A.L.}\textsuperscript{\textdagger}, Hammer M.F. Substructured population growth in the Ashkenazi Jews inferred with Approximate Bayesian Computation. Probabilistic Modeling in Genomics. 2018. Cold Spring Harbor, NY.

\item \textbf{Gladstein A.L.}\textsuperscript{\textdagger}, et al. Efficient pipeline for whole genome simulation and summary statistic calculation with flexible demographic models. Meeting of the American Society for Human Genetics. 2017. Orlando, FL.

\item \textbf{Gladstein A.L.}\textsuperscript{\textdagger}, et al. The effect of SNP array ascertainment bias on the distribution of runs of homozygosity lengths. Annual Meeting of the American Society for Human Genetics. 2015. Baltimore, MD. 

\end{rSection}

%----------------------------------------------------------------------------------------
%	Awards, Scholarships, & Grants
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards}

XSEDE Research allocation (250,000 CPU hrs) \hfill{\em 2020}\\
XSEDE Supplemental allocation (250,000 CPU hrs) \hfill{\em 2018, 2020}\\
Probabilistic Modeling in Genomics Grant (registration, meals, lodging) \hfill{\em 2018, 2019}\\
XSEDE Startup allocation (100,000 CPU hrs, 6,500 GPU hrs, 5.5 Tb storage) \hfill{\em 2019}\\
XSEDE Startup allocation (150,000 CPU hrs) \hfill{\em 2017}\\
Open Science Grid User School (travel, lodging, meals, cost of program) \hfill{\em 2017}\\
GPSC Travel Grant (\$761) \hfill{\em 2015, 2016, 2017} \\
University of Arizona Galileo Circle Scholarship (\$1,000) \hfill{\em 2015} \\
NIH Computational and Mathematical Modeling of Biological Systems Traineeship (\$71,064) \hfill {\em 2013-14}\\
NSF Integrative Graduate Education and Research Traineeship in Genomics (\$97,083) \hfill {\em 2011-13}\\
Society for Learning Unlimited Grant (\$2,000) \hfill {\em Fall 2009}\\
Study Abroad Enhancement Grant, Beloit College (\$250) \hfill {\em Spring 2009}\\
Beloit College Presidential Scholar (\$60,000) \hfill {\em 2007-2011}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Workshops
%----------------------------------------------------------------------------------------


\begin{rSection}{Workshops and Hackathons}

SMBE satellite meeting on Speciation Genomics, Tjarno, Sweden (3 days) \hfill{\em 06/2019}\\
NCBI RNA-Seq in the Cloud hackathon, Chapel Hill, NC (3 days) \hfill {\em 03/2019}\\
Cyber Carpentry, Chapel Hill, NC (2 weeks) \hfill {\em 06/2018}\\
XSEDE HPC Workshop: Big Data, Tucson, AZ (2 days) \hfill {\em 02/2018}\\
Open Science Grid User School, Madison, WI (1 week) \hfill {\em 07/2017}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Project Management
%----------------------------------------------------------------------------------------

\begin{rSection}{Project Management}

    Managed team of 5, including computer scientists, software engineer, and mathematician, \hfill {\em 2017}\\ 
    working on code development and high throughput computing for bioinformatics
    
    \end{rSection}

%----------------------------------------------------------------------------------------
%	Community Service
%----------------------------------------------------------------------------------------

\begin{rSection}{Community Service}

    \textbf{Mentoring}\\
    Undergraduate interns in computer science, Tucson, AZ \hfill {\em 2017}\\
    Arizona Assurance Mentor \hfill {\em 2012}
    
    \textbf{Judge}\\
    Graduate \& Professional Student Council Travel Grants, Tucson, AZ \hfill {\em 2012, 2016, 2017, 2018}\\
    Tucson Magnet High School Science Fair, Tucson, AZ \hfill {\em 2012, 2015}\\
    EEB Undergraduate Research Poster Session, Tucson, AZ \hfill {\em 2012}
    
    \end{rSection}

%----------------------------------------------------------------------------------------
%	Study Abroad
%----------------------------------------------------------------------------------------

\begin{rSection}{Study Abroad}

{\bf Lomonosov Moscow State University} \hfill Fall 2009 \\ 
{\em Biology Department} \hfill {\em Moscow, Russia}

{\bf Russian State University for the Humanities} \hfill Spring 2009 \\ 
{\em Russian Studies} \hfill {\em Moscow, Russia}

\end{rSection}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Other Activities
%----------------------------------------------------------------------------------------

\begin{rSection}{Other Activities}

{\bf Circus Arts} \hfill 2012 - present \\ 
{\em Aerial silks, aerial rope, lyra, flying trapeze, tightwire, handbalancing, contortion} 

{\bf Figure Skating} \hfill 1998 - 2013 \\ 
{\em Singles freestyle} 

\end{rSection}
%----------------------------------------------------------------------------------------


\end{document}